Extended Early Adulthood and Attitude Change

### 2024-07-23 manuscript/manuscript.Rmd
small updates

| Variables                      | M1       | M2       | M3       | M4       | M5       |
|------------|------------|------------|------------|------------|------------|
| Intercept                      | Y        | Y        | Y        | Y        | Y        |
| RE                             | Y        | Y        | Y        | Y        | Y        |
| Time                           | Y        | Y        | Y        | Y        | Y        |
| RE                             | Y        | Y        | Y        | Y        | Y        |
| Age Groups                     | Y        | Y        | Y        | Y        | Y        |
| RE                             | Y        | Y        | Y        | Y        | Y        |
| Duration                       | Y        | Y        | Y        | Y        | Y        |
| RE                             | Y        | Y        | Y        | Y        | Y        |
| Time \* Age Group              | Y        | Y        | Y        | Y        | Y        |
| RE                             | Y        | Y        | Y        | N        | N        |
| Time \* Duration               | Y        | Y        | Y        | Y        | Y        |
| RE                             | Y        | Y        | N        | N        | N        |
| Age Groups \* Duration         | Y        | Y        | Y        | Y        | N        |
| RE                             | Y        | Y        | N        | N        | N        |
| Age Groups \* Duration \* Time | Y        | N        | N        | N        | N        |
| RE                             | Y        | N        | N        | N        | N        |
|                                |          |          |          |          |          |
| BIC                            | 20714.39 | 20250.97 | 19996.61 | 19862.23 | 19845.22 |
| AIC                            | 19757.88 | 19675.82 | 19627.76 | 19643.42 | 19645.17 |

@@

| Col1             | Col2  | Col3 | Col4 |
|------------------|-------|------|------|
| Fixed Effects    |       |      |      |
| Intercept        | 17.45 |      |      |
| Time (decade)    | -0.26 |      |      |
| Age(26-33)       | -1.60 |      |      |
| Age(34-64)       | -3.17 |      |      |
| Age(65+)         | -4.10 |      |      |
| Duration (year)  | 1.13  |      |      |
| Time\*Age(26-33) | -0.09 |      |      |
| Time\*Age(34-64) | -0.54 |      |      |
| Time\*Age(65+)   | -1.33 |      |      |
|                  |       |      |      |
| Random Effects   | S.D.  |      |      |
| Intercept        | 5.35  |      |      |
| Time             | 1.14  |      |      |
| Duration         | 0.37  |      |      |
| Age(26-33)       | 0.89  |      |      |
| Age(34-64)       | 1.81  |      |      |
| Age(64+)         | 2.92  |      |      |

: Coefficient Estimates

>>>>

| Variables                      | M1       | M2       | M3       | M4       | M5       |
|--------------------------------|----------|----------|----------|----------|----------|
| Intercept                      | Y        | Y        | Y        | Y        | Y        |
| RE                             | Y        | Y        | Y        | Y        | Y        |
| Time                           | Y        | Y        | Y        | Y        | Y        |
| RE                             | Y        | Y        | Y        | Y        | Y        |
| Age Groups                     | Y        | Y        | Y        | Y        | Y        |
| RE                             | Y        | Y        | Y        | Y        | Y        |
| Duration                       | Y        | Y        | Y        | Y        | Y        |
| RE                             | Y        | Y        | Y        | Y        | Y        |
| Time \* Age Group              | Y        | Y        | Y        | Y        | Y        |
| RE                             | Y        | Y        | Y        | N        | N        |
| Time \* Duration               | Y        | Y        | Y        | Y        | Y        |
| RE                             | Y        | Y        | N        | N        | N        |
| Age Groups \* Duration         | Y        | Y        | Y        | Y        | N        |
| RE                             | Y        | Y        | N        | N        | N        |
| Age Groups \* Duration \* Time | Y        | N        | N        | N        | N        |
| RE                             | Y        | N        | N        | N        | N        |
|                                |          |          |          |          |          |
| BIC                            | 20714.39 | 20250.97 | 19996.61 | 19862.23 | 19845.22 |
| AIC                            | 19757.88 | 19675.82 | 19627.76 | 19643.42 | 19645.17 |

@@

|                         | Model 1      | Model 2      |
|-------------------------|--------------|--------------|
| **Fixed Effects**       |              |              |
| Intercept               | 17.77 (0.75) | 17.46 (0.77) |
| Time (decade)           | -0.01 (0.17) | -0.15 (0.17) |
| Age(26-33)              | -0.94 (0.35) | 0.42 (0.35)  |
| Age(34-64)              | -2.49 (0.37) | -0.82 (0.36) |
| Age(65+)                | -3.39 (0.48) | -1.70 (0.44) |
| Duration (year)         | 1.45 (0.10)  | 1.56 (0.10)  |
| Time\*Age(26-33)        | -0.02 (0.07) | 0.18 (0.07)  |
| Time\*Age(34-64)        | -0.51 (0.06) | -0.15 (0.06) |
| Time\*Age(65+)          | -1.38 (0.07) | -0.80 (0.07) |
| Duration\*Age(26-33)    | -0.17 (0.09) | -0.28 (0.08) |
| Duration\*Age(34-64)    | -0.38 (0.08) | -0.49 (0.07) |
| Duration\*Age(65+)      | -0.51 (0.02) | -0.58 (0.09) |
| Duration\*Time          | 0.14 (0.02)  | 0.15 (0.02)  |
| Ever married            |              | -0.89 (0.21) |
| Ever had child          |              | 0.26 (0.14)  |
| Child under 18 in house |              | 0.30 (0.10)  |
| Student                 |              | -0.57 (0.24) |
| Less than HS            |              | 2.80 (0.35)  |
| College degree          |              | -2.42 (0.24) |
|                         |              |              |
| **Random Effects**      | **S.D.**     | **S.D.**     |
| Intercept               | 5.99         | 6.24         |
| Time                    | 1.32         | 1.31         |
| Duration                | 0.50         | 0.50         |
| Age(26-33)              | 1.42         | 1.32         |
| Age(34-64)              | 2.26         | 1.99         |
| Age(64+)                | 3.06         | 2.41         |
| Ever married            |              | 1.60         |
| Ever had child          |              | 0.88         |
| Child under 18 in house |              | 0.67         |
| Student                 |              | 1.72         |
| Less than HS            |              | 1.04         |
| College degree          |              | 2.98         |

: Table \@ref(tab:2): Coefficient estimates from multilevel linear regressions of absolute change between responses on age group, duration, and question.
